The assessment of the ability of measurements, nowcasts, and forecasts to track changes

### 2024-04-16 paper.tex
Shorten intro C19-Nowcasting

The assessment of \ac{atc} is based on the measured, observed, or true and the predicted changes in a value of interest over a time horizon $l$.
The \textit{measured} change is straightforward to compute for all types of measurement, nowcast, or forecast.
Let $\mathbf{y} = (y_t)_{t=0}^T$ denote the actual values for nowcasting or forecasting, or gold standard measurements up to time $T$.
The sequence of observed changes is then given by the differences of values in $\mathbf{y}$ with horizon $l$, that is,
\begin{equation}\label{eq:diffy}
    \diffylt = (y_{t} - y_{t-l}) \quad \text{for}\ t = l, \dots, T.
\end{equation}

@@

In Germany, the seven-day hospitalization rate was established as a central steering measure in November 2021 during the COVID-19 pandemic, and the imposition of severe public restrictions was based on it~\citep{RobertKochInstitute2021}.
However, the publication of the definite hospitalization rate was substantially delayed and partially flawed for two main reasons.
First, the reporting process was delayed because – among other reasons – different authorities were involved in passing the data to the RKI~\citep{RobertKochInstitute2024}.
Second, the seven-day hospitalization rate allocated all COVID-19-related hospitalizations to the date of the first positive test~\parencite[for a detailed description, see][]{Wolffram2023}.
Nevertheless, as the seven-day hospitalization rate was considered an important indicator of how the pandemic developed, various organizations and institutions issued nowcasts.
The COVID-19-Nowcasting-Hub collected various nowcasts in a predefined setup, including the mean, median, and other quantiles of the predicted seven-day hospitalization rate~\citep{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024}.
For information on the model design, nowcast tasks, and the data submission guidelines, we refer to~\citet{Wolffram2023}.
Table~\ref{tab:app-covid-models} matches the abbreviations here to the respective names in the COVID-19-Nowcasting-Hub.
In addition to those nowcasts, \citet{Wolffram2023} construct two ensemble methods using the ensembles' mean or median.
We denote them by ENS-MEAN and ENS-MED.
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
We use the data from February 8, 2024, for the true values and focus on nowcasts for all inhabitants of Germany.
Figure~\ref{fig:app-covid-true-nowcast} in Appendix~\ref{sec:appendix-application-covid} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\citep{Tolksdorf2022}.

>>>>

The assessment of \ac{atc} is based on the measured/observed/true and the predicted changes in a value of interest over a time horizon $l$.
The \textit{measured} change is straightforward to compute for all types of measurement, nowcast, or forecast.
Let $\mathbf{y} = (y_t)_{t=0}^T$ denote the actual values for nowcasting or forecasting, or gold standard measurements up to time $T$.
The sequence of changes is then given by the differences of values in $\mathbf{y}$ with horizon $l$, that is,
\begin{equation}\label{eq:diffy}
    \diffylt = (y_{t} - y_{t-l}) \quad \text{for}\ t = l, \dots, T.
\end{equation}

@@

In Germany, the seven-day hospitalization rate was established as a central steering measure in November 2021 during the COVID-19 pandemic, and the imposition of severe public restrictions was based on it~\citep{RobertKochInstitute2021}.
However, the publication of the definite hospitalization rate was substantially delayed and partially flawed for two main reasons.
First, the reporting process was delayed because – among other reasons – different authorities were involved in passing the data to the RKI~\citep{RobertKochInstitute2024}.
Second, the seven-day hospitalization rate allocated all COVID-19-related hospitalizations to the date of the first positive test~\parencite[for a detailed description, see][]{Wolffram2023}.
The COVID-19-Nowcasting-Hub~\citep{ChairOfEconometricsAndStatisticsAtKarlsruheInstituteOfTechnology2024} collected various nowcasts in a predefined setup, including the mean, median and other quantiles of the predicted seven-day hospitalization rate~\parentext{for further information see~\citealp{Wolffram2023} and Table~\ref{tab:app-covid-models} for the abbreviations used}.
In addition to those nowcasts, \citet{Wolffram2023} construct two ensemble methods using the ensembles' mean or median.
We denote them by ENS-MEAN and ENS-MED.
In line with the initial study design, we consider the period from November 22, 2021, to April 29, 2022, as the evaluation period.
We use the data from February 8, 2024, for the true values and focus on nowcasts for all inhabitants of Germany.
Figure~\ref{fig:app-covid-true-nowcast} in Appendix~\ref{sec:appendix-application-covid} displays the true and nowcast data for the evaluation period.
The time comprises the fourth wave's end in December 2021 and nearly the entire fifth wave of the pandemic in Germany, lasting until May 28, 2022~\citep{Tolksdorf2022}.
